Title Goes Here

### 2020-02-25 paper/paper.tex
Move a 'TODO' into generated output
Add 'TODO' note about Oxford brackets
Improved wording of Oxford bracket 'TODO'
Describe section 6 in 'Structure' section

\begin{itemize}
  \item In section 3, an EDSL representation of pattern matching will be
    introduced.
  \item Sections 4 and 5 will discuss techniques for representing tail recursion
    and lambdas (respectively) in an EDSL. The tail recursion transformation
    does not depend on the rest of the EDSL and can be used separately from it.
  \item Section 7 describes the general control flow and specific syntactic
    transformations of the Core plugin.
\end{itemize}

\subsection{Translation Example} % TODO: Does it make sense for this to be a
                                 % subsection of the intro?

@@

@@

>>>>

\begin{itemize}
  \item In section 3, an EDSL representation of pattern matching will be
    introduced.
  \item Sections 4 and 5 will discuss techniques for representing tail recursion
    and lambdas (respectively) in an EDSL. The tail recursion transformation
    does not depend on the rest of the EDSL and can be used separately from it.
  \item Section 6 provides an implementation of \ttt{abs} which interprets an EDSL
    expression under the "standard" semantics (that is, applying this implementation
    to the result of the Core transformation will result in a program that behaves exactly
    the same as the original, untransformed, program).
  \item Section 7 describes the general control flow and specific syntactic
    transformations of the Core plugin.
\end{itemize}

\subsection{Translation Example} % TODO: 
\begin{tcolorbox}
  \textbf{TODO}: Does it make sense for this to be a subsection of the intro?
\end{tcolorbox}

@@

\begin{tcolorbox}
  \textbf{TODO}: Does this subsection use Oxford brackets in an appropriate way?
\end{tcolorbox}

@@

\clearpage
